---
title: "Single Samples"
author: "Sarah Musy, MSc"
date: "October 17, 2016"
output:
  ioslides_presentation:
    css: /media/sarah/6C428B2A428AF85A/Users/khadri/Documents/0_PhD/Teaching/4_HS16/Example/custom.css
    logo: /media/sarah/6C428B2A428AF85A/Users/khadri/Documents/0_PhD/Teaching/4_HS16/Example/logo.png
    transition: default
    widescreen: yes
  beamer_presentation: null
  slidy_presentation: default
subtitle: Lecture 4
bibliography: /media/sarah/6C428B2A428AF85A/Users/khadri/Documents/0_PhD/Teaching/4_HS16/Example/refs.bib
link-citations: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Definition
Sample = set of observation drawn from a population.  
```{r fig.width=8, fig.height=5,echo=FALSE}
library(png)
library(grid)
img <- readPNG("/media/sarah/6C428B2A428AF85A/Users/khadri/Documents/0_PhD/Teaching/4_HS16/4_Single_Samples/Sample.png")
 grid.raster(img)
```

## Data example
Size = 100 variables
```{r, echo=T}
dat <- read.csv("/media/sarah/6C428B2A428AF85A/Users/khadri/Documents/0_PhD/Teaching/4_HS16/4_Single_Samples/example.csv")
dat
```

## Summarizing the data

Can get very easily important information:

* Minimum and maximum value of the data
* Median and mean of the data
* <span style="color:red">First and third quartile<span> 

```{r, echo=T}
summary(dat)
```


## Quartile

Quartile means one quarter of the data

* **First quartile** = value of the data below which lie the 25% of the data = 25^th^ percentile
* **Second quartile** = median = 50% of the data are below the median = 50^th^ percentile = interquartile
* **Third quartile** = value of the data below which lie the 25% of the data = value of the data above which lie 25% of the data = 75^th^ percentile

```{r fig.width=7.5, fig.height=2.5,echo=FALSE}
library(png)
library(grid)
img <- readPNG("/media/sarah/6C428B2A428AF85A/Users/khadri/Documents/0_PhD/Teaching/4_HS16/4_Single_Samples/Quartile.png")
 grid.raster(img)
```

## Histogram

See two weeks ago.

```{r, echo=T}
hist(dat$y, main="Histogram", xlab="Data")
```



## Boxplot (1)

Can summarize all those information in a picture

* Bold horizontal bar = median
* Whiskers show maximum and minimum values
* Top and bottom of the box show the 75^th^ and 25^th^ percentile, respectively
* Whole box shows where the middle of the data lie

## Boxplot (2)
```{r, echo=T}
boxplot(dat)
```


